maASlin2

### 2019-12-06 scripts/06_lefse_res_ggplot.Rmd
update

# join all of the tables feature together
feature <- fns %>% 
  set_names(fns_name) %>% 
  map(~ read_tsv(., col_names = c('pathway','xx','direction','score','pval')) %>% 
        filter(!is.na(score))) %>% 
  bind_rows(.id = 'group') %>% 
  mutate(group = str_replace(group, 'pathway_abundace_pheno__','')) %>% 
  mutate(group = str_replace(group, '.res$','')) %>% 
  select(-xx, -pval)

@@

CR <- feature %>% 
  filter(group == 'CR') %>% 
  ggplot(aes(x = reorder(pathway, score), y = score, fill = direction)) +
            geom_bar( stat = 'identity') +
            coord_flip() +
            scale_color_manual(values = c('#ED0000', '#00468B'))  +
            scale_fill_manual(values = c('#ED0000', '#00468B')) +
            theme_classic() +
            theme(axis.title.y  = element_blank(), 
                  plot.title = element_text(size=all_title_fs),
                  axis.title.x = element_text(size=axis_text_fs),
                  axis.text.x = element_text(size=axis_text_fs),
                  legend.position='bottom') +
            labs(title = str_glue('Response to CR') ,
                 y = 'Score')+ 
            ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/humann2_shotgun/figs/lefse_results_ggplot_recreate/Response to CR.pdf'),  width = 12, device = 'pdf' )

>>>>

# join all of the tables feature together
feature <- fns %>% 
  set_names(fns_name) %>% 
  map(~ read_tsv(., col_names = c('pathway','xx','direction','score','pval')) %>% 
        filter(!is.na(score))) %>% 
  bind_rows(.id = 'group') %>% 
  mutate(group = str_replace(group, 'pathway_abundace_pheno__','')) %>% 
  mutate(group = str_replace(group, '.res$','')) %>% 
  dplyr::select(-xx, -pval)

@@

CR <- feature %>% 
  filter(group == 'CR') %>% 
  ggplot(aes(x = reorder(pathway, score), y = score, fill = direction)) +
            geom_bar( stat = 'identity') +
            coord_flip() +
            scale_color_manual(values = c('#925E9F', '#42B540'))  +
            scale_fill_manual(values = c('#925E9F', '#42B540')) +
            theme_classic() +
            theme(axis.title.y  = element_blank(), 
                  plot.title = element_text(size=all_title_fs),
                  axis.title.x = element_text(size=axis_text_fs),
                  axis.text.x = element_text(size=axis_text_fs),
                  legend.position='bottom') +
            labs(title = str_glue('Response to CR') ,
                 y = 'Score')+ 
            ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/humann2_shotgun/figs/lefse_results_ggplot_recreate/Response to CR.pdf'),  width = 12, device = 'pdf' )

### 2019-12-06 scripts/27_maASlin2.Rmd
update

```{r}
pw <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>% 
  dplyr::rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  dplyr::rename(pw = names(.)[1])  %>% 
  column_to_rownames('pw') %>% 
  as.matrix() %>% 
  t() %>% 
  as.data.frame()

fit_data <- Maaslin2(
    pw, pheno_final, '../data/maASlin2/pw', normalization  = 'NONE', transform = "LOG",  cores = 4, plot_heatmap = F,
    fixed_effects = c(

                      'Toxicity', 
                      'ICANS',
                      'Cytokine_Release_Syndrome',
                      'Disease_Class',
                      'Key__Patient_Disease_Status_at_CAR',
                      'ferritin',
                      'crp',
                      'IL_1_beta',
                      'IL_10',
                      'IL_6'),
    random_effects = c('MRN',
                       'CR',
                       'ORR', 
                       'Antibiotics_4_weeks_prior_to_CAR_T_cells', 
                       'sex',
                       'age'
                       ),
    standardize = FALSE)

fit_data <- Maaslin2(
    pw, pheno_final, '../data/maASlin2/pw', normalization  = 'NONE', transform = "LOG",  cores = 4, plot_heatmap = F,
    fixed_effects = c(  'sex',
                       'age'),

    standardize = FALSE)
```

>>>>

```{r}
pw <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>% 
  dplyr::rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  dplyr::rename(pw = names(.)[1])  %>% 
  # remove the things after the : so that its easier to see on the plot(the pathway name)
  mutate(pw = str_replace(pw, ':.+$','')) %>% 
  column_to_rownames('pw') %>% 
  as.matrix() %>% 
  t() %>% 
  as.data.frame()

fit_data <- Maaslin2(
    pw, pheno_final, '../data/maASlin2/pw', normalization  = 'NONE', transform = "LOG",  cores = 4, plot_heatmap = T,
    fixed_effects = c('Toxicity', 
                      'Cytokine_Release_Syndrome',
                      'ICANS',
                      'CR',
                      'ORR', 
                      'Disease_Class',
                      'Key__Patient_Disease_Status_at_CAR',
                      'Antibiotics_4_weeks_prior_to_CAR_T_cells', 
                      'ferritin',
                      'crp',
                      'IL_1_beta',
                      'IL_10',
                      'IL_6'),
    # random_effects = c('MRN',
    #                    'sex',
    #                    'age'),
    standardize = FALSE)

```{r}
trans <- log(pw[,'PWY-7456'] + 1)
```
